---
title: "Line graph of Fv/Fm results among different colonies"
format: html
theme: 
  light: zephyr
  dark: cyborg
toc: true
page-layout: full
number-sections: true
number-depth: 3
editor: visual
self-contained: true
---

# Import libraries

You can import libraries however you like. I just vibe with `pacman`.

```{r}
pacman::p_load(tidyverse,
               readxl, # Importing .xslx and other Excel-related data
               lubridate, # Tidy-managing date data 
               ggrepel)
```

# Import data

As you've seen, I imported `tidyverse`. I love tidyverse, if you don't, it's fine, but you might not appreciate this documentation.

```{r}
path <- 'pam-reconciled_2023-2024.xlsx'
data <- 
  path |> 
  excel_sheets() |> 
  set_names() |> 
  map(read_excel, path = path)
```

You might have noticed that the sheets are pooled into a list of dataframes. Separate them.

```{r}
iwalk(
  .x = data,
  .f = function(x, y) {
    x <- as.data.frame(x)
    y <- paste0('data_', y)
    assign(y, x, envir = globalenv())
    })
```

You now have different dataframes based on the name of your sheet.

# Amil

## Shape data

```{r}
data_amil <- 
  `data_Amil-PAM` |> 
  mutate(date_start = ymd(20231130),
         Date = ymd(Date)) |>
  mutate(days_exposure = Date - date_start,
         treatment = case_when(`Tank ID` %in% c("C", "G") ~ '29',
                               .default = '33')) |> 
   mutate(days_exposure = as.numeric(days_exposure)) |> 
  select(!c(10,11)) |> 
  as_tibble() |> 
  mutate(helper = paste0(`Fragment ID`, '_', days_exposure)) |> 
  mutate(`Fv/Fm=Y` = case_when(helper == '06ME_7' ~ 0,
                               .default = `Fv/Fm=Y`))
```

## Get top and bot 20% Fv/Fm (last day)

```{r}
data_amil_TopBot <- 
  data_amil |> 
  filter(treatment == '33',
         days_exposure == 7)|> 
  group_by(Colony) |> 
  summarise('Fv/Fm=Y' = mean(`Fv/Fm=Y`)) |> 
  arrange(desc(`Fv/Fm=Y`)) |> 
  mutate(ranking = 1:n(),
         heat_class = c(rep('High', 6),
                        rep('Intermediate', 18),
                        rep('Low', 6)))
```

## Plot

```{r}
data_amil_p <- 
  data_amil |> 
  filter(treatment == '33') |> 
  left_join(data_amil_TopBot |> 
              select(1,4), 
            by = 'Colony') |> 
  ggplot(aes(x = days_exposure,
             y = `Fv/Fm=Y`,
             group = Colony,
             color = heat_class)) +
  stat_summary(fun = mean,
               geom="line")  +
  theme_classic()

data_amil_p <- 
  data_amil |> 
  filter(treatment == '33') |> 
  left_join(data_amil_TopBot |> 
              select(1,4), 
            by = 'Colony') |> 
  ggplot(aes(x = days_exposure,
             y = `Fv/Fm=Y`,
             group = Colony,
             color = heat_class)) +
  geom_smooth(method = 'lm', se = F)  +
  theme_classic()
```
